---
title: "Using FishPhyloMaker to build phylogenies for bony fishes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using FishPhyloMaker to build phylogenies for bony fishes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Making a phylogeny of fish species using FishPhyloMaker package

In this article we will show how to obtain a phylogeny for a pool of species using FishPhyloMaker package. First of all, we need to install and read FishPhyloMaker package, that can be made using the following code:


```{r install_pkg, echo=TRUE, eval=FALSE}
devtools::install_github("GabrielNakamura/FishPhyloMaker", ref = "main")
```

We will use a data base that contain fish species from rivers and streams of neotropical region, this data are present in the package and can be easily accessed by typing:

```{r read_data, eval=FALSE, echo=TRUE} 
library(FishPhyloMaker)
data("fish_SAmerica")
```

`fish_SAmerica` correspond to a data frame containing the occurrence of 679 fish species at 37 basins in the neotropical region. To obtain a phylogenetic tree for these species we first need to format these data accordingly to enter in `FishPhyloMaker` function, that correspond to a data frame with three column containing the taxonomic information of each one of the 679 species. To obtain this data we will use the function `FishTaxaMaker` that finds for each name of species present in the `fish_SAmerica` data and checks if these names are found in [Fishbase]("https://www.fishbase.se/search.php"). 
Note that not all species was found in Fishbase data, so, the user must type manually, through an interactive process, the name of the Family and the Order of the species that was not found. The names must be typed sequentially, as in the following code.

```{r taxon_data, echo=TRUE, eval=FALSE}
taxon_data <- FishTaxaMaker(data = fish_SAmerica)
Loricariidae
Siluriformes
Anostomidae 
Characiformes
Anostomidae 
Characiformes
Anostomidae 
Characiformes
Serrasalmidae
Characiformes
Auchenipteridae
Siluriformes
Auchenipteridae
Siluriformes
Auchenipteridae
Siluriformes
```

This function will return a data frame with three columns and the same number of species present in `fish_SAmerica` data, and now this data can be used in `FishPhyloMaker` function to generate the phylogenetic tree for these species. In this example we will set the argument return.insertions = TRUE, since we want to know at which level of insertion each species was inserted in the process. Like `FishTaxaMaker` function, `FishPhyloMaker` also have a interactive process of insertion in which the user must inform at which genus or family the species must be inserted in the mega-tree. There are three options: 

1. **Insert the species near to a given genus/family**: To insert the species near to a specific genus/family, the user must       type the name of the genus (or family) at which the species must be inserted;

2. **Insert the species between two genus/families**: To insert the species between two different genus or families, the user 
    must type the names of the two genus/families separated by a blank space;

3. **Insert at the root of the family/order**: To insert the species at the node that corresponds to the family (or order), the user must type the name of the family.

These three options are shown in the following code:

*NOTE* - The function can take several minutes to run depending on the number of species that must be inserted.

```{r phylo_make, eval=FALSE, echo=TRUE}
phylo_fish_SAmerica <- FishPhyloMaker(data = taxon_data, return.insertions = T)
Serrasalmidae
Acanthicus
Schizodon
Liosomadoras
Hemiancistrus
Ctenolucius
Roeboexodon Exodon
Leporinus
Gymnotus
Loricariichthys
Anostomus
Furcodontichthys
Lasiancistrus
Leporinus
Schizodon Hypomasticus
Batrochoglanis
Pseudolithoxus
Leporinus
Anodus
Paralonchurus
Pachypops
Vandellia Paravandellia
Pachyurus
Anostomus
Sternarchorhamphus
Vandellia
Odontognathus
Exallodontus
Myleus
Gnathodolus
Trachelyopterus
Hemiodontichthys
Rhinelepis
Pseudohemiodon
Schizodon
Gnathodolus
Panaque Panaqolus
Pseudacanthicus Leporacanthicus
Hypopomidae
Sternarchogiton
Platyurosternarchus
Gymnocorymbus
Schizodon
Synbranchidae
Ageneiosus
Asterophysus
Trachelyopterus
Ageneiosus
```

The result is a list containing two objects, a phylogenetic tree and a dataframe indicating at which level each species was inserted in the phylogeny. We can directly plot the phylogenetic tree

```{r plot_phylo, eval=FALSE, echo=TRUE}
plot(phylo_fish_SAmerica$Phylogeny, cex = 0.3)
```



